Import Jaz data

### 2023-12-08 Code/JazDataImport.Rmd
Removed lubridate removed knit output

---
title: "Import Jaz data"
output: html_notebook
---

```{r libraries}
#library(dplyr) 
library(tidyverse)
library(lubridate)
library(googledrive)
library(googlesheets4)

@@

MultiCultiPAR <- read.csv(file.path(DataIn, "MultiCulti_PAR.csv"))

>>>>

---
title: "Import Jaz data"
---

```{r libraries}
#library(dplyr) 
library(tidyverse)
library(googledrive)
library(googlesheets4)

@@

MultiCultiPAR <- read_csv(file.path(DataIn, "MultiCulti_PAR.csv"))
